Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Updated graphs and tables with sha256d data, and added text in Results chapter for why sha256 single is not included

\section{Measurements of Tahoe operations}
%\vskip -1.5em % This is to fit in two graphs on one page including heading

% How much time is spent on hashing versus total time of
%   uploading/downloading

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

@@

@@

BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file, but on small files, SHA-256 is faster by a large
margin. The difference between the slowest (JH) and the fastest (BLAKE)
algorithm is 229.92s when uploading the one gigabyte file.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading10001Bfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading10001Bfiles.pdf}
    \caption{Figures for hash operations of 1000 1B files.}
    \label{fig:graph:10001b}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading1001KBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading1001KBfiles.pdf}
    \caption{Figures for hash operations of 100 1KB files.}
    \label{fig:graph:1001kb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading501MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading501MBfiles.pdf}
    \caption{Figures for hash operations of 50 1MB files.}
    \label{fig:graph:501mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading5100MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading5100MBfiles.pdf}
    \caption{Figures for hash operations of five 100MB files.}
    \label{fig:graph:5100mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading11GBfile.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading11GBfile.pdf}
    \caption{Figures for hash operations of one 1GB file.}
    \label{fig:graph:11gb}
\end{figure}

>>>>

\section{Measurements of Tahoe operations}

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:1001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

@@

\ac{SHA}-256 (single) is not included in the graphs, because the results were
exactly the same as for the \ac{SHA}-256d used in Tahoe-\ac{LAFS}.

@@

BLAKE, \ac{BMW}, Shabal and Simd outperform \ac{SHA}-256d when both uploading
and downloading a 1GB file, but on small files, \ac{SHA}-256d is faster by a
large margin. The difference between the slowest (JH) and the fastest (BLAKE)
algorithm is 229.92s when uploading the 1GB file.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhileuploading1001Bfiles.pdf}
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhiledownloading1001Bfiles.pdf}
    \caption{Figures for hash operations of 100 1B files.}
    \label{fig:graph:1001b}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhileuploading1001KBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhiledownloading1001KBfiles.pdf}
    \caption{Figures for hash operations of 100 1KB files.}
    \label{fig:graph:1001kb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhileuploading501MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhiledownloading501MBfiles.pdf}
    \caption{Figures for hash operations of 50 1MB files.}
    \label{fig:graph:501mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhileuploading5100MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhiledownloading5100MBfiles.pdf}
    \caption{Figures for hash operations of five 100MB files.}
    \label{fig:graph:5100mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhileuploading11GBfile.pdf}
    \includegraphics[width=0.9\columnwidth]
        {graphs/Timespenthashingwhiledownloading11GBfile.pdf}
    \caption{Figures for hash operations of one 1GB file.}
    \label{fig:graph:11gb}
\end{figure}
